Predicting Solid State Material Platforms for Quantum Technologies

### 2021-12-17 paper.tex
Updates from Overleaf

>>>>

In summary, using various
data extraction tools for a number of materials science databases, we have obtained databases consisting of over 25.000 materials. The information from the databases has then been converted into nearly 5000 physics-informed features.
After these steps with fine-tuning and selection of entries  for our data sets we are now ready to apply machine learning methods in order to classify materials as potential candidates for quantum technologies.
